Computation and comparison of the stable Northeastern US marine boundary layer

### 2020-12-01 Paper/results.tex
copied over new plots and updated results.tex

%%%%%%%%%%% z=20m snapshot pics %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \fxnote{label plots using pstricks: 5m/s on top, 15m/s on bottom} \\
  \includegraphics[width=3.0in]{figures/snapshots/05ms/velh_mag_z20.png}
  \includegraphics[width=3.0in]{figures/snapshots/05ms/velz_z20.png} \\

  \includegraphics[width=3.0in]{figures/snapshots/10ms/velh_mag_z20.png}
  \includegraphics[width=3.0in]{figures/snapshots/10ms/velz_z20.png} \\

  \includegraphics[width=3.0in]{figures/snapshots/15ms/velh_mag_z20.png}
  \includegraphics[width=3.0in]{figures/snapshots/15ms/velz_z20.png} \\
  \caption{ \label{fig:SnapshotsZ20} Snapshots of the horizontal
    velocity and vertical velocity, taken at t=20,000 seconds of the
    simulations at height z=20m.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

>>>>

%%%%%%%%%%% z=20m snapshot pics %%%%%%%%%%%%%%%%%%%%%%%%%
% Created in Postprocessing/ABLStats/AMRWind_NaluWind_stable_AllWS_2p5Cubed.ipynb
\begin{figure}[hbt!]
  \centering
  \fxnote{label plots using pstricks: 5m/s on top, 15m/s on bottom} \\
  \includegraphics[width=3.0in]{figures/snapshots/05ms/velh_mag_z20_samelimits.png}
  \includegraphics[width=3.0in]{figures/snapshots/05ms/velz_z20_samelimits.png} \\

  \includegraphics[width=3.0in]{figures/snapshots/10ms/velh_mag_z20_samelimits.png}
  \includegraphics[width=3.0in]{figures/snapshots/10ms/velz_z20_samelimits.png} \\

  \includegraphics[width=3.0in]{figures/snapshots/15ms/velh_mag_z20_samelimits.png}
  \includegraphics[width=3.0in]{figures/snapshots/15ms/velz_z20_samelimits.png} \\
  \caption{ \label{fig:SnapshotsZ20} Snapshots of the horizontal
    velocity and vertical velocity, taken at t=20,000 seconds of the
    simulations at height z=20m.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
